---
title: "Marketing Analytics Dashboard"
format:
  html:
    toc: true
    toc-location: right
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

## Dashboard Overview

This dashboard highlights selected marketing performance metrics from my portfolio projects. The goal is to show how marketing data can be organized, visualized, and used to understand campaign performance.

The dashboard focuses on customer response, revenue, profit, and project-level marketing insights.

---

## Key Performance Metrics

```{r}
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(dplyr)
library(knitr)

kpi_data <- data.frame(
  Metric = c(
    "Super Soakerz Customers",
    "Super Soakerz Revenue",
    "Super Soakerz Profit",
    "Portfolio Projects",
    "Main Career Focus"
  ),
  Result = c(
    "18 customers",
    "$63.00",
    "$49.50",
    "4 featured projects",
    "Marketing Strategy"
  )
)

kable(
  kpi_data,
  col.names = c("Metric", "Result"),
  align = "c"
)
```

---

## Project Summary

```{r}
#| echo: false
#| message: false
#| warning: false

project_summary <- data.frame(
  Project = c(
    "Super Soakerz",
    "LA Galaxy Campaign",
    "Tesla Strategy Analysis",
    "Google Organizational Analysis"
  ),
  Focus = c(
    "Campus service marketing",
    "Sports marketing and fan engagement",
    "Brand strategy and sustainability",
    "Company culture and leadership"
  ),
  Skills = c(
    "Promotion, pricing, customer outreach",
    "Audience targeting, campaign strategy",
    "Positioning, corporate strategy",
    "Research, communication, analysis"
  )
)

kable(
  project_summary,
  col.names = c("Project", "Marketing Focus", "Skills Demonstrated"),
  align = "l"
)
```

---

## Super Soakerz Financial Results

```{r}
#| echo: false
#| message: false
#| warning: false

financials <- data.frame(
  Category = c("Revenue", "Estimated Profit"),
  Amount = c(63.00, 49.50)
)

ggplot(financials, aes(x = Category, y = Amount)) +
  geom_col(width = 0.6) +
  labs(
    title = "Super Soakerz Revenue and Estimated Profit",
    subtitle = "Financial results from the student-led marketing campaign",
    x = "",
    y = "Amount ($)"
  ) +
  theme_minimal(base_size = 13)
```

---

## Customer Response

```{r}
#| echo: false
#| message: false
#| warning: false

customer_data <- data.frame(
  Metric = c("Customers Served"),
  Count = c(18)
)

ggplot(customer_data, aes(x = Metric, y = Count)) +
  geom_col(width = 0.5) +
  labs(
    title = "Customer Response",
    subtitle = "Total customers served during the Super Soakerz campaign",
    x = "",
    y = "Number of Customers"
  ) +
  theme_minimal(base_size = 13)
```

---

## Marketing Skills Breakdown

```{r}
#| echo: false
#| message: false
#| warning: false

skills <- data.frame(
  Skill = c(
    "Marketing Strategy",
    "Brand Engagement",
    "Customer Outreach",
    "Data Visualization",
    "Professional Presentation"
  ),
  Level = c(5, 4, 4, 4, 4)
)

ggplot(skills, aes(x = reorder(Skill, Level), y = Level)) +
  geom_col(width = 0.6) +
  coord_flip() +
  labs(
    title = "Marketing Skills Demonstrated",
    subtitle = "Skills reflected across portfolio projects",
    x = "",
    y = "Skill Strength"
  ) +
  theme_minimal(base_size = 13)
```

---

## Dashboard Insights

The dashboard shows that my strongest portfolio areas are marketing strategy, campaign planning, customer outreach, and brand engagement. The Super Soakerz project provides a real example of applying marketing concepts to a small service-based campaign, while the LA Galaxy project connects directly to my interest in sports marketing.

Together, these projects show my ability to combine marketing strategy, audience understanding, data visualization, and professional communication.

---

## Key Takeaway

This dashboard demonstrates my ability to organize marketing project results, present key metrics clearly, and use visuals to communicate campaign performance. It supports my career interests in sports marketing, brand strategy, and data-driven marketing.