---
title: "Marketing Analytics "
subtitle: "Quarto Revealjs Presentation"
author: "Briana Maximino"
format:
  revealjs:
    theme: simple
    slide-number: true
    transition: slide
    width: 1600
    height: 900
    scrollable: true
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
---

## RPE Marketing Analytics Project

### Technical Portfolio Presentation

**Briana Maximino**  
Business Administration — Marketing Management  
Cal Poly Pomona

---

## Project Overview

This project analyzed student survey data to better understand how instructor helpfulness may relate to students’ likelihood of participating in a course evaluation survey.

The goal was to practice using **R, Quarto, data wrangling, visualization, and interpretation** in a marketing research style project.

---

## Research Question

**How does perceived instructor helpfulness relate to students’ likelihood of participating in a survey?**

This question connects to marketing analytics because it focuses on understanding audience behavior and what factors may influence participation.

---

## Why This Matters

Survey participation is important because organizations, schools, and brands often rely on feedback to make better decisions.

If students are more likely to participate when they view instructors as helpful, then communication, trust, and positive experiences may play an important role in response behavior.

---

## Tools Used

- **R** for data analysis
- **Quarto** for report building
- **ggplot2** for visualizations
- **dplyr** for data wrangling
- **haven** for reading SPSS data
- **knitr** for clean tables

---

## Data Wrangling Process

The data first had to be cleaned and prepared before analysis.

Main steps included:

- Loading the dataset
- Selecting variables related to instructor helpfulness and survey participation
- Converting labeled responses into numeric values
- Removing missing responses
- Grouping responses by helpfulness level
- Calculating average participation scores

---

## Example R Code

```{r}
#| eval: false

library(haven)
library(dplyr)
library(ggplot2)

rpe_data <- read_sav("RPE - Combined-2019-12-19.sav")

rpe_clean <- rpe_data |>
  mutate(
    R_Helpful_num = as.numeric(as_factor(R_Helpful)),
    RPE_LikelyParti_num = as.numeric(as_factor(RPE_LikelyParti))
  ) |>
  filter(
    !is.na(R_Helpful_num),
    !is.na(RPE_LikelyParti_num)
  )
```

---

## Variables Used

| Variable | Meaning |
|---|---|
| `R_Helpful` | Student rating of instructor helpfulness |
| `RPE_LikelyParti` | Student likelihood of participating in the survey |
| `R_Helpful_num` | Numeric version of instructor helpfulness |
| `RPE_LikelyParti_num` | Numeric version of survey participation likelihood |

---

## Operational Scale

The variables were treated as numeric rating scale variables.

Higher values represented stronger agreement or higher levels of the measured concept.

This made it possible to compare average participation scores across different helpfulness levels.

---

## Summary Table Code

```{r}
#| eval: false

summary_table <- rpe_clean |>
  group_by(R_Helpful_num) |>
  summarise(
    Average_Participation = mean(RPE_LikelyParti_num, na.rm = TRUE),
    Count = n()
  ) |>
  filter(Count >= 10)
```

---

## Visualization Code

```{r}
#| eval: false

ggplot(summary_table, aes(
  x = R_Helpful_num,
  y = Average_Participation
)) +
  geom_col() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Instructor Helpfulness and Survey Participation",
    x = "Instructor Helpfulness",
    y = "Average Likelihood to Participate"
  ) +
  theme_minimal()
```

---

## Main Finding

The analysis showed a positive relationship between instructor helpfulness and students’ likelihood of participating in the survey.

As instructor helpfulness increased, the average likelihood to participate also increased.

---

## Interpretation

This suggests that students may be more willing to provide feedback when they have a positive experience with the instructor.

For marketing research, this connects to the idea that trust, experience, and perceived value can affect whether people choose to respond or engage.

---

## Skills Demonstrated

This project demonstrates my ability to:

- Work with survey data
- Clean and transform variables in R
- Use the pipe operator
- Create summary tables
- Build visualizations with ggplot2
- Interpret data findings
- Present analysis using Quarto

---

## Connection to Marketing Analytics

Marketing analytics is not only about sales data. It also includes understanding behavior, attitudes, participation, and engagement.

This project helped me practice using data to explain why people may be more likely to respond, participate, or engage with a survey.

---

## Key Takeaway

The RPE project helped me build confidence using R and Quarto to turn raw survey data into a clear research finding.

It shows my ability to combine technical tools with marketing research thinking.

---

## Thank You

**Briana Maximino**  
Marketing Portfolio  
R / Quarto / Marketing Analytics