---
title: "Super Soakerz Marketing Campaign"
format:
  html:
    toc: true
    toc-location: right
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

## Project Overview

Super Soakerz was a student-led car window washing service created for a marketing course at Cal Poly Pomona. The project focused on building a service brand from scratch, promoting it to students, and measuring real customer response through campus outreach.

The campaign positioned Super Soakerz as a convenient, affordable, and student-run service for busy commuter students who wanted a quick way to clean their car windows while on campus.

## Objective

The main objective was to create and promote a small service-based business while applying marketing concepts such as target market selection, positioning, pricing, promotion, and customer engagement.

## Target Audience

The target audience was Cal Poly Pomona students, especially commuter students between the ages of 18 and 25 who drive to campus and may not have time to regularly clean their car windows.

## My Role

For this project, I contributed to the campaign planning, customer outreach, service promotion, and overall marketing strategy. I helped shape the project’s messaging around convenience, affordability, and student-to-student service.

## Campaign Strategy

The campaign used simple and direct messaging to attract students on campus. The strategy focused on:

- Promoting the service as quick and affordable
- Reaching students through in-person campus outreach
- Building trust by presenting the service as student-run
- Using clear pricing and simple service benefits
- Emphasizing convenience for commuter students

## Key Results

| Metric | Result |
|---|---:|
| Customers Served | 18 |
| Revenue Generated | $63.00 |
| Estimated Profit | $49.50 |
| Main Audience | Cal Poly Pomona commuter students |
| Service Type | Car window washing |

## Campaign Performance Dashboard

```{r}
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(dplyr)
library(knitr)

results <- data.frame(
  Metric = c("Customers Served", "Revenue Generated", "Estimated Profit"),
  Value = c(18, 63, 49.50)
)

kable(
  results,
  col.names = c("Metric", "Value"),
  align = "c"
)
```

## Revenue and Profit Overview

```{r}
#| echo: false
#| message: false
#| warning: false

financials <- data.frame(
  Category = c("Revenue", "Estimated Profit"),
  Amount = c(63.00, 49.50)
)

ggplot(financials, aes(x = Category, y = Amount)) +
  geom_col(width = 0.6) +
  labs(
    title = "Super Soakerz Revenue and Profit",
    subtitle = "Financial results from the student-led campaign",
    x = "",
    y = "Amount ($)"
  ) +
  theme_minimal(base_size = 13)
```

## Customer Response

```{r}
#| echo: false
#| message: false
#| warning: false

customers <- data.frame(
  Category = c("Customers Served"),
  Count = c(18)
)

ggplot(customers, aes(x = Category, y = Count)) +
  geom_col(width = 0.5) +
  labs(
    title = "Customer Response",
    subtitle = "Total customers served during the campaign",
    x = "",
    y = "Number of Customers"
  ) +
  theme_minimal(base_size = 13)
```

## Marketing Skills Demonstrated

This project helped demonstrate several marketing skills, including:

- Target market identification
- Service positioning
- Pricing strategy
- Campus promotion
- Customer engagement
- Team collaboration
- Basic performance tracking

## What I Learned

Through this project, I learned how important it is to clearly communicate the value of a service. Even with a simple business idea, the marketing message, pricing, and customer interaction all affect whether people are willing to participate.

The project also helped me understand how marketing works in a real setting. Instead of only creating a plan, the team had to actually promote the service, speak with potential customers, and adjust based on customer response.

## Key Takeaway

Super Soakerz showed me how marketing strategy can turn a simple student service into a real campaign. The project helped me build experience in promotion, customer communication, teamwork, and measuring results.